---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## omni

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/coatless/omni.svg?branch=master)](https://travis-ci.com/coatless/omni)
<!-- badges: end -->

The goal of omni is to provide pre-defined schemes to use with omnigraffle
from _R_.

The idea for the package and some initial code structure came from
[Bob Rudis'](https://rud.is/b/) post regarding 
[Spelunking macOS ‘ScreenTime’ App Usage with R](https://rud.is/b/2019/10/28/spelunking-macos-screentime-app-usage-with-r/).

### Installation

You can install the released version of omni from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("omni")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("coatless/omni")
```

### Usage

To use `omni`, load the package with: 

```{r example}
library(omni)
```


Todo: Add an example with `data.frame` and `list`.

